Asymmetric continuous prediction bands for assessing the validity of smooth biomechanical curve data

### 2021-08-24 paper.Rmd
Add missing plots for shock data

#### Heteroscedasticity across the signal length (Robinson et al., 2014)

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}

```

@@

data <- example_data(dat = "non_gaussian", dir.data)
floa <- floa_rcb(data, n.boot, ver = "v2")
plot_loa(data, floa, central.tendency = "mean")
```

@@

<!-- https://mjskay.github.io/ggdist/articles/lineribbon.html -->
<!-- In general I have found that there is no one method that consistently works well on all datasets. No matter the method, intervals often become problematic above 50%, hence the default .width for curve_interval() is 0.5 (unlike the default for point_interval(), which is 0.95). In any case, caution when using these intervals is advised. -->

>>>>

#### Heteroscedasticity across the signal length

@@

@@

data <- example_data(dat = "non_gaussian", dir.data)
floa <- floa_rcb(data, n.boot, ver = "v2")
plot_loa(data, floa, central.tendency = "mean")

data <- example_data(dat = "shock", dir.data)
floa <- floa_rcb(data, n.boot, ver = "v2")
plot_loa(data, floa, central.tendency = "mean")
```

@@

<!-- Limitations of curvewise intervals -->
<!-- https://mjskay.github.io/ggdist/articles/lineribbon.html -->
<!-- One challenge with curvewise intervals is that they can tend to be very conservative, especially at moderate-to-large intervals widths. -->
<!-- Notice how noisy the curvewise intervals are. In addition, because a number of curves tend to start low and end high (or vice versa), above 50%, the bands rapidly expand to cover almost all of the curves in the sample, regardless of coverage level. -->
<!-- In general I have found that there is no one method that consistently works well on all datasets. No matter the method, intervals often become problematic above 50%, hence the default .width for curve_interval() is 0.5 (unlike the default for point_interval(), which is 0.95). In any case, caution when using these intervals is advised. -->
